### 2022-04-23 msz_gal_2.tex
renaming

\begin{figure}[H]
    \centering
    \includegraphics[width=0.4\linewidth]{46/relax.png}
    \caption{Ukázka činnosti funkce \textit{relax}.}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\linewidth]{46/example_bellman_ford_p1.pdf}
    \caption{Příklad, část 1.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\linewidth]{46/example_bellman_ford_p2.pdf}
    \caption{Příklad, část 2.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\linewidth]{46/example_bellman_ford_p3.pdf}
    \caption{Příklad, část 3.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\linewidth]{46/example_bellman_ford_p4.pdf}
    \caption{Příklad, část 4.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\linewidth]{46/example_bellman_ford_p5.pdf}
    \caption{Příklad, část 5.}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\linewidth]{46/example_dijkstra_p1.pdf}
    \caption{Příklad, část 1.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\linewidth]{46/example_dijkstra_p2.pdf}
    \caption{Příklad, část 2.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\linewidth]{46/example_dijkstra_p3.pdf}
    \caption{Příklad, část 3.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\linewidth]{46/example_dijkstra_p4.pdf}
    \caption{Příklad, část 4.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\linewidth]{46/example_dijkstra_p5.pdf}
    \caption{Příklad, část 5.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\linewidth]{46/example_dijkstra_p6.pdf}
    \caption{Příklad, část 6.}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.4\linewidth]{gal_2/relax.png}
    \caption{Ukázka činnosti funkce \textit{relax}.}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\linewidth]{gal_2/example_bellman_ford_p1.pdf}
    \caption{Příklad, část 1.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\linewidth]{gal_2/example_bellman_ford_p2.pdf}
    \caption{Příklad, část 2.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\linewidth]{gal_2/example_bellman_ford_p3.pdf}
    \caption{Příklad, část 3.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\linewidth]{gal_2/example_bellman_ford_p4.pdf}
    \caption{Příklad, část 4.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\linewidth]{gal_2/example_bellman_ford_p5.pdf}
    \caption{Příklad, část 5.}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\linewidth]{gal_2/example_dijkstra_p1.pdf}
    \caption{Příklad, část 1.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\linewidth]{gal_2/example_dijkstra_p2.pdf}
    \caption{Příklad, část 2.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\linewidth]{gal_2/example_dijkstra_p3.pdf}
    \caption{Příklad, část 3.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\linewidth]{gal_2/example_dijkstra_p4.pdf}
    \caption{Příklad, část 4.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\linewidth]{gal_2/example_dijkstra_p5.pdf}
    \caption{Příklad, část 5.}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\linewidth]{gal_2/example_dijkstra_p6.pdf}
    \caption{Příklad, část 6.}
\end{figure}
